Marker_identification_Benchmark

### 2023-10-27 Demo_marrow_facs.Rmd
cellmarkerdb_change

library("Seurat")
library("SeuratWrappers")
```

@@

### Visualize Module on Cell embeddings

```{r, fig.width=20, fig.asp=1}
pl = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module)))
})
plot_grid(plotlist = pl,ncol = 5) # may takes long time to plot
```

## Step3: Identify Celltype-specific activated Modules

```{r}
# Create one-hot vector of Cell Type
one_hot_matrix <- sapply(unique(cell_label), function(x) as.integer(cell_label == x))

# Order Cell Type based on its centroid in Featurespace
Idents(tiss) = cell_label
ordered_cell_types <- unique(cell_label)[hclust(dist(t(sapply(unique(cell_label), function(x) colMeans(Embeddings(tiss, reduction = "pca")[WhichCells(tiss, idents = x), ,drop = FALSE]) ))))$order]

# Calculate Jaccard index between module activity & cell type
jaccard_index <- apply(cell_block, 2, function(module_col) {
  apply(one_hot_matrix, 2, function(one_hot_col) {
    1 - philentropy::distance(rbind(module_col,one_hot_col), method = "jaccard", mute.message=TRUE)
  })
})
jaccard_index = jaccard_index[rev(ordered_cell_types),]
rm(ordered_cell_types)
```

### Visualize Heatmap of Jaccard Index Matrix

```{r}
pheatmap(jaccard_index,
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white")))(99))
```

### Visualize How CellType-Module is Matched on Cell Embeddings

For each cell type, select the most specific modules for visualization (maximum jaccard index)

```{r}
tiss@meta.data = cbind(tiss@meta.data,one_hot_matrix)
jaccard_thred = 0.4

# Get Module plot
pl_module = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module)))
})
names(pl_module) = levels(gene_partition)

# Get CellType One-hot plot
pl_ct = lapply(colnames(one_hot_matrix),function(ct){
  FeaturePlot_custom(value = as.factor(one_hot_matrix[,ct]), coord = visual_space, value_name = "Indicator",title_name = ct)
})
names(pl_ct) = colnames(one_hot_matrix)

pl <- lapply(rownames(jaccard_index)[rev(order(apply(jaccard_index,1,max)))], function(celltype){
  if(max(jaccard_index[celltype,]) > jaccard_thred){
    p1 = pl_ct[[celltype]]
    module_name = colnames(jaccard_index)[which.max(jaccard_index[celltype,])]
    p2 = pl_module[[module_name]]
    p = as.ggplot(p1) + as.ggplot(p2) + plot_annotation(paste0("Jaccard Index: ",round(jaccard_index[celltype,module_name],2)))
    p
  }
})
```

### Annotate Each Celltype-specific activated Modules with its corresponding Celltypes

```{r}
module_celltype = apply(jaccard_index,2,function(x){paste(names(which(x > 0.4)),collapse = ",")})
```

## Save Intermediate data
```{r}
save(gene_partition,dist,gene_hree,cell_block,jaccard_index,file = "./marrow_result/module_result.rdata")
```

@@

## Step5: Generate Gene Module Annotation Table

```{r}
df_module = data.frame(Module = levels(gene_partition))
df_module[,"Gene"] = unlist(lapply(levels(gene_partition),function(x){paste(names(gene_partition)[gene_partition == x],collapse = ",")}))
df_module[,"celltype"] = module_celltype[levels(gene_partition)]
df_module[top_go_clusters,"GO_description"] = unlist(lapply(top_enrich_go,function(x) paste(x[['Description']],collapse = ",")))
df_module[top_pathway_clusters,"Pathway_description"] = unlist(lapply(top_enrich_pathway,function(x) paste(x[['Description']],collapse = ",")))
df_module[is.na(df_module)] = ""
write.csv(df_module,file = "module_description.csv",row.names = FALSE)
```

>>>>

library("Seurat")
library("SeuratWrappers")
library("pheatmap")
library("ggplot2")
library("ggplotify")
```

@@

## Step3: Identify Celltype-specific activated Modules
```{r}
cell_label = as.factor(tiss$cell_ontology_class)
abbrev = levels(cell_label)
abbrev[grepl("T cell",abbrev)] = "T cell"
abbrev[grepl("natural killer",abbrev)] = "NK cell"
abbrev[abbrev == "B cell"] = "Cd3e+ Klrb1+ B cell"
abbrev[grepl("Slamf1-positive",abbrev)] = "Slamf1+ MPC"
abbrev[grepl("Slamf1-negative",abbrev)] = "Slamf1- MPC"
abbrev[grepl("common lymphoid",abbrev)] = "CLP"
abbrev[grepl("megakaryocyte",abbrev)] = "MEP"
abbrev[grepl("hematopoietic",abbrev)] = "HSC"
abbrev[grepl("hematopoietic",abbrev)] = "HSC"
abbrev[grepl("granulocyte monocyte",abbrev)] = "GMP"
# abbrev[grepl("granulocytopoietic",abbrev)] = "G-poiesis"
names(abbrev) = levels(cell_label)
levels(cell_label) = abbrev[levels(cell_label)]

# Create one-hot vector of Cell Type
one_hot_matrix <- sapply(unique(cell_label), function(x) as.integer(cell_label == x))

# # Order Cell Type based on its centroid in Featurespace
# Idents(tiss) = cell_label
# ordered_cell_types <- unique(cell_label)[hclust(dist(t(sapply(unique(cell_label), function(x) colMeans(Embeddings(tiss, reduction = "pca")[WhichCells(tiss, idents = x), ,drop = FALSE]) ))))$order]

# Calculate Jaccard index between module activity & cell type
jaccard_index <- apply(cell_block, 2, function(module_col) {
  apply(one_hot_matrix, 2, function(one_hot_col) {
    1 - philentropy::distance(rbind(module_col,one_hot_col), method = "jaccard", mute.message=TRUE)
  })
})
# jaccard_index = jaccard_index[rev(ordered_cell_types),]
# rm(ordered_cell_types)
```

### Jaccard Index Heatmap
```{r}
thred = 0.4
jaccard_index_pruned = jaccard_index[apply(jaccard_index,1,max) > thred,]
jaccard_index_pruned = jaccard_index_pruned[,apply(jaccard_index_pruned,2,max) > thred]

colnames(jaccard_index_pruned) = paste0("M",colnames(jaccard_index_pruned))
jaccard_index_pruned = jaccard_index_pruned[names(sort(apply(jaccard_index_pruned,1,which.max))),]
p = pheatmap(t(jaccard_index_pruned),
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white")))(99),
         angle_col = 45,legend_title = "Jaccard Index",silent = TRUE,
         cellwidth = 15, cellheight = 10)
p_jaccard = as.ggplot(p) + coord_fixed()
ggsave(filename = "jaccard_heatmap.png", plot = p_jaccard, width = 5, height = 10)
```

### CellType-Module Matched on Cell Embeddings
For each cell type, select the most specific modules for visualization (maximum jaccard index)
```{r}
# Get Module plot
pl_module = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module))) + scale_color_gradient(limits = c(0, 1),low = "lightgrey", high = "blue")
})
names(pl_module) = levels(gene_partition)

# Get CellType One-hot plot
pl_ct = lapply(colnames(one_hot_matrix),function(ct){
  FeaturePlot_custom(value = as.factor(one_hot_matrix[,ct]), coord = visual_space, value_name = "Indicator",title_name = ct) + scale_color_manual(values = c("0" = "lightgrey", "1" = scales::hue_pal()(1)))
})
names(pl_ct) = colnames(one_hot_matrix)

ct_module_match = apply(jaccard_index_pruned,1,function(x) colnames(jaccard_index_pruned)[which.max(x)])
ct_module_match = gsub("M","",ct_module_match)

pl <- lapply(seq(length(ct_module_match)),function(i){
    (pl_module[[ct_module_match[i]]] + NoLegend())/
    (pl_ct[[names(ct_module_match)[i]]] + NoLegend())
})

ncol = 7
legend_module = get_legend(pl_module[[1]])
legend_ct = get_legend(pl_ct[[1]])
bottom_row = plot_grid(
  plot_grid(plotlist = pl[(ncol+1):length(pl)],ncol = length(pl) - ncol), 
  plot_grid(legend_module, legend_ct, ncol = 1),
  rel_widths = c((ncol-1),1),nrow = 1)
p = plot_grid(
  plot_grid(plotlist = pl[1:ncol], ncol = ncol),
  bottom_row,
  ncol = 1)
rm(bottom_row)

ggsave(filename = "ct-specific-module.png", plot = p, width = 35, height = 20)
```

### Annotate Each Celltype-specific activated Modules with its corresponding Celltypes
```{r}
module_celltype = apply(jaccard_index,2,function(x){paste(names(which(x > 0.4)),collapse = ",")})
```

## Transferability of Modules
### Load Data & Calculate Module Activity
```{r}
if (!file.exists('droplet_Marrow_seurat_tiss.Robj')) {
   # If load url doesn't work, please download it and load from your working directory
  options(timeout=6000)
  download.file("https://figshare.com/ndownloader/files/13092380",
                destfile = 'droplet_Marrow_seurat_tiss.Robj', method = 'libcurl')
 }
load('droplet_Marrow_seurat_tiss.Robj')
tiss_droplet <- UpdateSeuratObject(tiss_droplet)

# path <- "/data/ruiqi/local_marker/dataset/tabular_muris/"
# tissue_name = "marrow_droplet"
# tiss_droplet <- readRDS(sprintf("%s%s.rds",path,tissue_name))

feature_space_droplet = as.matrix(tiss_droplet@reductions$pca@cell.embeddings[,1:n_dim])
dat_droplet = as.matrix(tiss_droplet[["RNA"]]@data)

knn = 10; major_vote = 5
A = Symmetric_KNN_graph(knn = knn, feature_space = feature_space_droplet)$'adj_matrix'
cell_block_loop = lapply(1:100,function(loop){
  GMM_subsampling(seed = loop, gene_partition, expr_dat = dat_droplet, cell_kNN_graph = A, major_vote)
})
cell_block_prop = Reduce(`+`, cell_block_loop) / length(cell_block_loop)
cell_block_droplet = cell_block_prop
```

### Calculate Jaccard Index
```{r}
cell_label = tiss_droplet$cell_ontology_class
cell_label[!cell_label %in% names(abbrev)] = NA
cell_label = setNames(abbrev[cell_label],names(cell_label))

one_hot_matrix <- sapply(unique(na.omit(cell_label)), function(x) as.integer(cell_label == x))
one_hot_matrix[is.na(one_hot_matrix)] = 0

jaccard_index_droplet <- apply(cell_block_droplet, 2, function(module_col) {
  apply(one_hot_matrix, 2, function(one_hot_col) {
    1 - philentropy::distance(rbind(module_col,one_hot_col), method = "jaccard", mute.message=TRUE)
  })
})
```
### Check whether the modules specific in FACs still specific in droplet
```{r}
module_selected = unlist(apply(jaccard_index[rownames(jaccard_index_droplet),],1,function(x) colnames(jaccard_index)[which(x > 0.4)]))
module_selected = module_selected[order(as.numeric(module_selected))]
ct_selected = rownames(jaccard_index_pruned)[rownames(jaccard_index_pruned)%in% rownames(jaccard_index_droplet)] 
jaccard_index_pruned = jaccard_index_droplet[ct_selected,module_selected]
colnames(jaccard_index_pruned) = paste0("M",colnames(jaccard_index_pruned))

p = pheatmap(t(jaccard_index_pruned),
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white")))(99),
         angle_col = 45,legend_title = "Jaccard Index",silent = TRUE,
         cellwidth = 15, cellheight = 10)
p_jaccard = as.ggplot(p) + coord_fixed()
ggsave(filename = "fig-cross-dataset-jaccard.png", plot = p_jaccard, width = 5, height = 10)
```

## Save Intermediate data
```{r}
save(gene_partition,dist,gene_hree,cell_block,cell_block_droplet,jaccard_index,file = "./marrow_result/module_result.rdata")
```

@@

## Step5: Generate Gene Module Annotation Table
```{r}
df_module = data.frame(Module = levels(gene_partition))
df_module[,"Gene"] = unlist(lapply(levels(gene_partition),function(x){paste(names(gene_partition)[gene_partition == x],collapse = ",")}))
df_module[,"celltype"] = module_celltype[levels(gene_partition)]
df_module[top_go_clusters,"GO_description"] = unlist(lapply(top_enrich_go,function(x){
  des = x[["Description"]]
  paste(des[!is.na(des)],collapse = ",")
}
))
df_module[top_pathway_clusters,"Pathway_description"] = unlist(lapply(top_enrich_pathway,function(x){
  des = x[["Description"]]
  paste(des[!is.na(des)],collapse = ",")
}))
df_module[is.na(df_module)] = ""
write.csv(df_module,file = "./marrow_result/module_description.csv",row.names = FALSE)
```

## Module-analysis
```{r}
df_module = read.csv("./marrow_result/module_description.csv")
df_module$'multi-celltype' = NA
df_module$'note' = NA
```

### Cell Cycle Modules
```{r}
library(gprofiler2)
mmus_s = gorth(cc.genes.updated.2019$s.genes, source_organism = "hsapiens", target_organism = "mmusculus")$ortholog_name
mmus_g2m = gorth(cc.genes.updated.2019$g2m.genes, source_organism = "hsapiens", target_organism = "mmusculus")$ortholog_name
tiss = CellCycleScoring(tiss, s.features = mmus_s, 
                        g2m.features = mmus_g2m, set.ident = FALSE)
p = as.ggplot(DimPlot(tiss,group.by = "Phase", cols = c("grey",scales::hue_pal()(3)[2:3])))

# df_module[c(16,18,17,31,32),'note'] = "cell_cycle"

p = plot_grid(plotlist = c(list(p),pl_module[c(16,18,17,31,32)]),ncol = 3)
ggsave(filename = "fig-cellcycle.png", plot = p, width = 15, height = 10)
```

### Multi-resolution Modules
```{r}
ct_prob_per_module = do.call(rbind,lapply(unique(cell_label),function(x){apply(cell_block[cell_label == x,],2,median)}))
rownames(ct_prob_per_module) = unique(cell_label)
ct_num_per_module = sort(apply(ct_prob_per_module,2,function(x)sum(x > 0.5)))

m = 19
df_module[m,"celltype"] = paste0(names(which(ct_prob_per_module[,m] > 0.5)),collapse = ",")

df_module[54,"multi-celltype"] = c("T/NK/NKT")
df_module[27,"multi-celltype"] = c("Progenitor/NK/NKT")
df_module[33,"multi-celltype"] = c("Progenitor/basophil/granulocytopoietic/half-granulocyte")
df_module[46,"multi-celltype"] = c("monocyte/granulocytopoietic/half-granulocyte")
df_module[48,"multi-celltype"] = c("monocyte/granulocytopoietic/granulocyte")
df_module[49,"multi-celltype"] = c("monocyte/macrophage/granulocytopoietic/granulocyte")
df_module[55,"multi-celltype"] = c("NK")
df_module[56,"multi-celltype"] = c("NK")
df_module[13,"multi-celltype"] = c("B")
df_module[50,"multi-celltype"] = c("monocyte/granulocytopoietic/granulocyte/basophil")
df_module[28,"multi-celltype"] = c("Progenitor")
df_module[9,"multi-celltype"] = c("immature/naive B")
df_module[11,"multi-celltype"] = c("late pro/pre B")
df_module[7,"multi-celltype"] = c("late pro/pre B")
df_module[44,"multi-celltype"] = c("granulocytopoietic/half-granulocyte")
df_module[47,"multi-celltype"] = c("granulocytopoietic/granulocyte")
df_module[52,"multi-celltype"] = c("T")
df_module[53,"multi-celltype"] = c("macrophage/NK")
df_module[1,"multi-celltype"] = c("monocyte/macrophage/granulocyte monocyte progenitor cell")
df_module[20,"multi-celltype"] = c("granulocytopoietic/Progenitor")
df_module[c(42,35),"multi-celltype"] = c("below-half-granulocyte/monocyte")
df_module[c(36,38),"multi-celltype"] = c("granulocyte monocyte progenitor cell/monocyte")
df_module[2,"multi-celltype"] = c("granulocyte monocyte progenitor cell/macrophage")
df_module[4,"celltype"] = c("granulocyte monocyte progenitor cell")
df_module[c(5,6,43),"note"] = "subtype"
```

### Joint-CT Module visualization
```{r}
level0_module = c(46,13,54,28,38)
# level1_module = c(45,41,51,24,14,4,37,3,8,10,52,56)
ncol = length(level0_module)
legend_module <- get_legend(pl_module[[1]])
prow <- cowplot::plot_grid(plotlist = lapply(pl_module[level0_module],function(x) x + NoLegend()), ncol = ncol)
p = plot_grid(prow, legend_module, rel_widths = c(ncol, .2))

ggsave(filename = "fig-joint-module.png", plot = p, width = 25, height = 5)
```

### Subtype Investigation
```{r}
# coldef = setNames(colorRampPalette(brewer.pal(12, "Paired"))(length(unique(cell_label))),unique(cell_label))
# 
# centroids <- aggregate(. ~ cell_label, data = as.data.frame(Embeddings(tiss, "tsne")), FUN = mean)
# p <- DimPlot(tiss, group.by = "cell_ontology_class",label = FALSE, cols = coldef) + theme_void() + NoLegend() + ggtitle("Bone Marrow FACS")
# p = p + 
#   geom_text_repel(data = centroids, aes(x = tSNE_1, y = tSNE_2, label = cell_label, color = cell_label),
#                    box.padding = 0.3, point.padding = 0.3, segment.color = 'grey50',max.overlaps = 100)

p <- DimPlot(tiss, group.by = "cell_ontology_class",label = FALSE, cols = setNames(scales::hue_pal()(2),c("late pro-B cell","granulocyte"))) + ggtitle("pre-annotated cell types")
pl_module_subtype =

pl1 = FeaturePlot(tiss,features = names(gene_partition)[gene_partition %in% c(5,6)][c(1:3,7,9)],ncol = 5,order = TRUE)
pl2 = FeaturePlot(tiss,features = names(gene_partition)[gene_partition == 43][1:5],ncol = 5,order = TRUE)
pl_module_subtype = lapply(pl_module[c(5,6,43)],function(x) x + scale_color_gradient(low = "lightgrey", high = "blue"))

combined_p = plot_grid(p,plotlist = pl_module_subtype,ncol = 2) + as.ggplot(pl1) + as.ggplot(pl2) + plot_layout(design = "\nAAAABBBBBBB\nAAAACCCCCCC\n")

ggsave(filename = "fig-subtype.png", plot = combined_p, width = 35, height = 10)
```

### 2023-10-27 Marker_identfication_benchmark.Rmd
cellmarkerdb_change

# Define Ground truth Marker
## Criterion1: Fold-change
For each gene, sorting cell types by mean expression for each gene and computing fold changes between consecutive types, take the maximum value among the N-1 fold change values, given N cell types.
```{r}
path = "./benchmark_result/"
# tissue_name = "marrow_facs"
```

@@

max_logfc = sort(max_logfc,decreasing = TRUE)
write.table(max_logfc,file = paste0(path,tissue_name,"_ground_truth_c1.txt"))
```
## Criterion2: CellMarkerDB
Downloaded marker from http://bio-bigdata.hrbmu.edu.cn/CellMarker/CellMarker_download_files/file/Cell_marker_Seq.xlsx
PanglaoDB: https://panglaodb.se/markers/PanglaoDB_markers_27_Mar_2020.tsv.gz and exclude genes that reported only once
```{r}
# Load CellMarkerDB
cell_marker_db = readxl::read_xlsx("/data/ruiqi/local_marker/dataset/Cell_Marker/Cell_marker_All.xlsx") %>% filter(species == "Mouse") %>% filter(tissue_class == "Bone marrow") %>% filter(!is.na(cellontology_id)) %>% filter(!is.na(PMID)) %>% mutate(gene_name1 = marker) %>% mutate(gene_name2 = Symbol) %>% select(c("gene_name1","gene_name2")) %>% group_by(across(everything())) %>% dplyr::summarise(count = n(), .groups = "drop") %>% filter(count > 1)

@@

# AUROC
```{r}
path = "./benchmark_result/"
# tissue_name = "marrow_facs"
df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
```
```{r}
max_logfc = read.table(paste0(path,tissue_name,"_ground_truth_c1.txt")) %>% rownames()
celldb_marker = read.table(paste0(path,tissue_name,"_ground_truth_c2.txt"))[,1]

gt_list = c(lapply(seq(50,1000,50),function(x) max_logfc[1:x]),list(celldb_marker))
names(gt_list) = c(paste0("Top",seq(50,1000,50)),"CellMarkerDB")
df = do.call(rbind,lapply(1:length(gt_list),function(i){
  true_marker = gt_list[[i]]
  df_benchmark$"gt" = 0
  df_benchmark[true_marker,"gt"] = 1

@@

>>>>

# Define Ground truth Marker
## Criterion1: Fold-change
For each gene, sorting cell types by mean expression for each gene and computing fold changes between consecutive types, take the maximum value among the N-1 fold change values, given N cell types.
```{r}
path = "./benchmark_result/"
tissue_name = "marrow_facs"
```

@@

max_logfc = sort(max_logfc,decreasing = TRUE)
write.table(max_logfc,file = paste0(path,tissue_name,"_ground_truth_c1.txt"))
```
## Criterion2: CellMarkerDB
Downloaded marker from http://bio-bigdata.hrbmu.edu.cn/CellMarker/CellMarker_download_files/file/Cell_marker_Seq.xlsx
<!-- PanglaoDB: https://panglaodb.se/markers/PanglaoDB_markers_27_Mar_2020.tsv.gz and exclude genes that reported only once -->
```{r}
# Load CellMarkerDB
cell_marker_db = readxl::read_xlsx("/data/ruiqi/local_marker/dataset/Cell_Marker/Cell_marker_All.xlsx") %>% filter(species == "Mouse") %>% filter(tissue_class == "Bone marrow") %>% filter(!is.na(cellontology_id)) %>% filter(!is.na(PMID)) %>% mutate(gene_name1 = marker) %>% mutate(gene_name2 = Symbol) %>% select(c("gene_name1","gene_name2")) %>% group_by(across(everything())) %>% dplyr::summarise(count = n(), .groups = "drop") %>% filter(count >= 1) # Lung, Pancreas

@@

# AUROC
```{r}
path = "./benchmark_result/"
# tissue_name = "marrow_facs"
df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))

method_ls = c("lmd","haystack","hotspot","marcopolo","semi","wilcox_default","wilcox_no_filter","hvg")
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v3 default", "Seurat v3 Wilcoxon unfiltered","HighlyVariableGenes"),method_ls)
```
```{r}
max_logfc = read.table(paste0(path,tissue_name,"_ground_truth_c1.txt")) %>% rownames()
celldb_marker = read.table(paste0(path,tissue_name,"_ground_truth_c2.txt"))[,1]
gt_list = c(lapply(seq(50,1000,50),function(x) max_logfc[1:x]),list(celldb_marker))
names(gt_list) = c(paste0("Top",seq(50,1000,50)),"CellMarkerDB")

# AUC table
df = do.call(rbind,lapply(1:length(gt_list),function(i){
  true_marker = gt_list[[i]]
  df_benchmark$"gt" = 0
  df_benchmark[true_marker,"gt"] = 1

@@

```{r}
# Concordance table
do.call(cbind,lapply(gt_list[c(2,21)],function(true_marker){
  df_benchmark$"gt" = 0
  df_benchmark[true_marker,"gt"] = 1
  apply(df_benchmark,2,function(x){
    sum(df_benchmark[order(x),"gt"][1:100])
  })
}))

# AUC curve
p = ggplot(roc_df, aes(x = FPR, y = TPR, color = label)) +
  geom_line(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray") + labs(title = sprintf("CellMarkerDB (%d genes)",length(true_marker)),
     x = "False Positive Rate",
     y = "True Positive Rate") +  scale_colour_manual(values= coldef)
```
